Did COVID-19 Induce A Strenuous Effect on the 311 Non-Emergency Services System?

### 2022-07-17 draft_v2.Rmd
summary stats

```{r library, warning=FALSE, message = FALSE}
#load library
library(dplyr)
library(reshape2)
library(openxlsx)
library(car)
library(ggplot2)
library(hrbrthemes)
library(viridis)
library(ggpattern)
library(plm)
library(haven)
library(texreg)
library(lfe)
#install.packages("devtools")
#library(devtools)
#install_github('arilamstein/choroplethrZip@v1.3.0')
library(choroplethrZip)

@@

# create covid related calls 
dat = dat %>%
  mutate(

@@

```{r}
#summary stats

>>>>

```{r library, warning=FALSE, message = FALSE}
#load library
library(dplyr)
library(reshape2)
library(openxlsx)
library(car)
library(ggplot2)
library(hrbrthemes)
library(viridis)
library(ggpattern)
library(plm)
library(haven)
library(texreg)
library(lfe)
#install.packages("devtools")
#library(devtools)
#install_github('arilamstein/choroplethrZip@v1.3.0')
library(choroplethrZip)
library(kableExtra)

@@

#remove data not avail
dat = dat %>% filter(CATEGORY != "Data Not Available")
# create covid related calls 
dat = dat %>%
  mutate(

@@

```{r}
#summary stats
ss01 = dat %>% summarize(obs = n(),
                 min = min(DAYTOCLOSE,na.rm=T),
                 q25 = quantile(DAYTOCLOSE,0.25,na.rm=T),
                 mean = mean(DAYTOCLOSE,na.rm=T),
                 q75 = quantile(DAYTOCLOSE,0.75,na.rm=T),
                 max = max(DAYTOCLOSE,na.rm=T)
                 ) %>% mutate(var = "all")

ss02 = dat %>% 
  group_by(allcovid) %>%
  summarize(obs = n(),
                 min = min(DAYTOCLOSE,na.rm=T),
                 q25 = quantile(DAYTOCLOSE,0.25,na.rm=T),
                 mean = mean(DAYTOCLOSE,na.rm=T),
                 q75 = quantile(DAYTOCLOSE,0.75,na.rm=T),
                 max = max(DAYTOCLOSE,na.rm=T)
                 ) %>% rename(var = allcovid)

ss03 = dat %>% 
  group_by(CATEGORY) %>%
  summarize(obs = n(),
                 min = min(DAYTOCLOSE,na.rm=T),
                 q25 = quantile(DAYTOCLOSE,0.25,na.rm=T),
                 mean = mean(DAYTOCLOSE,na.rm=T),
                 q75 = quantile(DAYTOCLOSE,0.75,na.rm=T),
                 max = max(DAYTOCLOSE,na.rm=T)
                 ) %>% rename(var = CATEGORY)

ss04 = dat %>% 
  group_by(CREATEYR) %>%
  summarize(obs = n(),
                 min = min(DAYTOCLOSE,na.rm=T),
                 q25 = quantile(DAYTOCLOSE,0.25,na.rm=T),
                 mean = mean(DAYTOCLOSE,na.rm=T),
                 q75 = quantile(DAYTOCLOSE,0.75,na.rm=T),
                 max = max(DAYTOCLOSE,na.rm=T)
                 ) %>% rename(var = CREATEYR)

ss = rbind(ss01,ss02,ss04,ss03)
ss
# ss %>% 
#   kable() %>%
#   kable_styling()
